---
title: "Homework 4"
output:
  html_document:
    df_print: paged
---

```{r}
library(datasets)
library(dplyr)
library(ggplot2)
?ChickWeight
```

1.
```{r}
weight0 <- ChickWeight %>%
  group_by(Diet) %>%
  summarize(avg = mean(weight), sd= sd(weight))
  

print(weight0)
```

2.
```{r}
complete <- ChickWeight %>%
  group_by(Chick) %>%
  mutate(num_measurements=n()) %>%
  filter(num_measurements > 11)

# complete <- ungroup(complete) ...based off of piazza i don't think we need to ungroup here 
print(head(complete,3))

```

3.
```{r}

complete <- ungroup(complete)
foo <- complete %>%
  group_by(Chick) %>%
  mutate(weightgain = weight - weight[Time == 0.0])

print(head(foo, 3))

```

4.
```{r}

foo2 <- foo %>% filter(Time == 21)

p <- ggplot(foo2, aes(x=reorder(Diet, weightgain, FUN = median), y=weightgain)) + geom_boxplot() + expand_limits(y=0)

print(p) 
```

The most effective diet was diet 3, as chicks gained more weight from that Diet in particular. Saying that though there was still a particularly high range of values (some higher than the max in Diet 4) for the other diets in quantiles outside of the 50%. This can be seen for Diet 2 in particular.

5. Using numerical and graphical analysis

```{r}
# Numerical Analysis
foo3 <- foo2 %>%
  arrange(weightgain)

least_weight_gained <- head(foo3, 1)
most_weight_gained <- tail(foo3,1) 
print(least_weight_gained)
print(most_weight_gained)

# Graphical Analysis

p<-ggplot(data=ChickWeight, aes(x=Chick, y=weight)) +
  geom_bar(stat="identity")
print(p)
```

The least weight gained chick was on Diet 2, and was Chick 21.
The chick that gained the most weight was on Diet 3, and was Chick 40.

6.
```{r}

all_peeps <- complete %>%
  group_by(Chick) %>%
  filter(Time == 0) %>%
  arrange(weight)

# Chick 25 and Chick 24

small_peep <- complete %>%
  filter(Chick == 25)

large_peep <- complete %>%
  filter(Chick == 24)

avg_weight <- ChickWeight %>%
  group_by(Time) %>%
  mutate(avg_weight = mean(weight))
  

ggplot() + 
  geom_line(data = small_peep, aes(x = Time, y = weight), color = "blue") +
  geom_line(data = large_peep, aes(x = Time, y = weight), color = "red") + 
  # 7
  geom_line(data = avg_weight, aes(x = Time, y = avg_weight), color = "black")


```



